\papertitle

### 2021-03-10 source_separation/paper/paper.tex
Add to future work, small edits to sep methods

		\subsection{Separation Methods}
	We consider source separation models trained to tackle two distinct separation problems. The first is music source separation (Open-Unmix, Demucs, ConvTasnet). For these architectures, we used models that were pre-trained on the MUSDB18 dataset~\cite{MUSDB18}. Thus, these models outputs 4 stereo tracks, that correspond to broad instrumental categories defined in the SiSEC 2018 Mus evaluation campaign~\cite{Stoter_SiSEC}, i.e. \textit{vocals, drums, bass} and \textit{other}. The audio sources we consider in this work are often non-musical, but we hope that these source separation methods can still improve the orchestration by separating other types of sound in a musically meaningful way.
	The second one is universal sound separation (TDCN++, NMF), which \cite{tdcnpp} defines as \textit{separating mixtures of arbitrary sounds of different types}.

@@

	As we stated in Section \ref{sec:conclusions}, we believe that one of the reasons the supervised methods did not perform as well is because of the data they were trained on. Therefore, a natural next step is to train these models ourselves with sounds that are more applicable to computer-assisted orchestration.

>>>>

		\subsection{Separation Methods}
	We consider source separation models trained to tackle two distinct separation problems. The first is music source separation (OpenUnmix, Demucs, ConvTasnet). For these architectures, we used models that were pre-trained on the MUSDB18 dataset~\cite{MUSDB18}. Thus, these models output 4 stereo tracks that correspond to broad instrumental categories defined in the SiSEC 2018 Mus evaluation campaign: \textit{vocals, drums, bass} and \textit{other}~\cite{Stoter_SiSEC}. Although the audio sources we consider in this work are often non-musical, we hope that these source separation methods can still improve the orchestration by separating other types of sound in a musically meaningful way.
	The second type of model we tested are ones trained for universal sound separation (TDCN++, NMF), which \cite{tdcnpp} defines as \textit{separating mixtures of arbitrary sounds of different types}.

@@

	As we stated in Section \ref{sec:conclusions}, we believe that one of the reasons the supervised methods did not perform as well is because of the data they were trained on. Therefore, a natural next step is to train these models ourselves with sounds that are more applicable to computer-assisted orchestration. This would be a dataset similar to the samples that make up our targets, instead of the music tracks that the models were trained on.
